\cbstart
The study results showed that the transition mostly supported pointing out the advantages and disadvantages of the thematic maps. The drawbacks of each type of visualisation were found by at least 64\%. Furthermore, the strengths of a dot map and a choropleth map were found at least 71\%. The most widespread types of thematic maps are dot and choropleth maps. This could indicate a correlation with the slightly better results of those two types. The proportional symbol map and the Pseudo-Demers cartogram had less positive results. 50\% of the participants could point out the advantages of a proportional symbol map and only 21\% those of a cartogram.
\cbend

The score indicating the usefulness of the transition overall is relatively low compared to the mostly positive results of the binary questions. However, the mean score of the transition (3,21) indicates, that the transition was received slightly positive. Thanks to the feedback the participants provided, it is possible to say that more animation interaction and different types of transitions would significantly affect the score in a positive way. Some suggested implementing play and pause features to keep track of particular stops, whereas other ones asked for more variety in transitions. Therefore, the feedback can be used for future work which could lead to a higher score for the transition.

However, the study results also go in line with the statements made by \citeauthor{Munzner2014}. She said using motion as a visual encoding channel is a very effective one but very hard to master \iacite{Munzner2014}. Every person has different perception of motion, e.g. the speed of moving objects. This was also observable in the conducted study. Participants with more experience in the domain of visualisation used a higher particle speed compared to inexperienced ones.

\cbstart
The conducted user study would yield better results with a different study design. Conducting a study between subject would yield results with better comparability among each other. Furthermore, participants should be set a task for each transition type. This would result in more detailed findings, e.g. the effectiveness of each transition.
\cbend

Thus, relating the primary research question of this thesis with the study results suggest that transitions do help in pointing out strengths and weaknesses of thematic maps. The generalised research question of which tasks can be supported by particle aggregation in a thematic map would need further investigation with different use cases in order to answer it properly.