\section{Visualization}
Visualization is not a new phenomenon. It has been used in maps, scientific drawings and data plots for over a thousand years. Examples of this are the map of China and the famous map of Napoleon's invasion of Russia which are explained later in detail. Most of the concepts learned in devising these images carry over in a straight forward manner to computer visualization \iacite{Tufte:1990}.

This first part of this chapter provides an overview important milestones in the history of visualization. The history is followed by a definition of visualization in literature and a definition of visualization for this thesis. This yields to the basis to be able to define different types of visualizations like \ac{InfoVis}, \ac{SciVis} and \ac{GeoVis} (which are all explained in detail in chapter \ref{s:definitions-types} on page \pageref{s:definitions-types}). The definitions are followed by an essential discussion about the basic principles of data visualizations and differnet types of visualizations.

The second part of tis chapter uses the knowledge of the first part to describe exploratory data analysis in conjunction with visualizations. This is also done with some pratical applications and examples which are also used to segue into the next chapter which deals with \ac{GeoVis}. It is used to show different types and use cases of \ac{GeoVis}. Therefore some related works are mentioned and their problems are mentioned.

\subsection{History}
\label{s:history}
\input{chapters/visualizations/history}

\subsection{Definition}
\label{s:definition}
\input{chapters/visualizations/definition}

\subsection{Varieties of visualizations}
\label{s:definitions-types}
\input{chapters/visualizations/definitions}

\subsection{Basic Principles}
\label{s:basics}
\input{chapters/visualizations/basics}

\subsection{Exploratory data analysis}
\label{s:eda}
% This topic could be taken to subsume the two main focii: statistical graphics, and thematic cartography.

% Both of these are concerned with the visual representation of quantitative and categorical data, but driven by different representational goals. Cartographic visualization is primarily concerned with representation constrained to a spatial domain; statistical graphics applies to any domain in which graphical methods are employed in the service of statistical analysis. There is a lot of overlap, but more importantly, they share common historical themes of intellectual, scientific, and technological development.

% In addition, cartography and statistical graphics share the common goals of visual representation for exploration and discovery. These range from the simple mapping of locations (land mass, rivers, terrain), to spatial distributions of geographic characteristics (species, disease, ecosystems), to the wide variety of graphic methods used to portray patterns, trends, and indications.



\subsection{Geovisualization}
% In modern geovisualization software, such data are represented using both traditional cartographic techniques based on the use of colours, textures, symbols, and diagrams; and using computer-enabled techniques such as map animation and interactive 3D views. Moreover, maps are used in combination with nongeographic visualization techniques such as scatterplots or parallel coordinates. The use of multiple interactively linked views providing different perspectives into the data has become a kind of standard in geovisualization. However, a number of problems have yet to be solved, such as the scalability of geovisualization tools and their usability.

% Introduction

% Related Work

%     Visualizations

%         History

%         Definition

%         Basic principles

%         Exploratory data analysis
%             - theoretical statistics
%             - exploratory data analysis with visualizations

%         Definitions of differnt types of visualizations
%             - information visualization
%             - scientific visualization
%             - geovisualization

%         Geovisualization
%             - partical applications
%             - examples and use-cases

%             - aggregation in geovisualization
%             - related work

%     Transitions in Visualizations
%         - examples and use-cases
%         - related work

%         - Transitions in Geovisualizations
%             - related work and concepts

%     Particle-based related work

%     Summary of problems and missing transitions in related work

% Implementation

% Results

% Discussion & Outlook
