When designing maps, there is one difference to be made: designing maps for print versus the internet. For the first case, the design is for map readers, whereas for the latter case, it is for map users. The difference between readers and users lays in the interaction. This chapter focuses on map designed for the internet and therefore allowing a lot more interaction. Users do not only interact but also manipulate web maps. Interaction for print maps would be moving a paper map closer or further away to one's eyes, or trim specific parts with scissors and so forth. The weakness of this kind of interaction is that the data on the map stays the same. However, zooming, selecting and moving a map on the internet actually allows for adapting the data shown \iacite{Muehlenhaus2014}.

As already mentioned in chapter \ref{s:definitions-types} on page \pageref{s:definitions-types}, \citeauthor{Shneiderman1996} published an often cited mantra \iacite{Shneiderman1996}:
\begin{quote}
Overview first, zoom and filter, then details on demand.
\end{quote}

% MISSING BOOK: Information Visualization: Design for Interaction Spence 2007
% This mantra can also be used as a guideline for creating web maps with interaction.
% % Spence2007
% introduces a so called action cycle, which models an interactive exploration process of data. Small datasets, as well as complex and dynamic data can make use of this process in order to properly implement and integrate interaction.

% TODO - CHECK IF ENOUGH WORDS

The first part of this chapter will introduce some basic interaction methods and concepts. The second part will build upon the knowledge of the first part and maps the basic concepts to today's implementations with the focus on interaction with thematic maps.

\subsubsection{Overview First, Focus + Context}
\input{chapters/methods/interaction/focus-context}

\subsubsection{Details on Demand}
\input{chapters/methods/interaction/dod}

\subsubsection{Multiple Views, Linking \& Brushing}
\label{s:linking-brushing}
\input{chapters/methods/interaction/linking}

\subsubsection{Animations and Transitions}
\input{chapters/methods/interaction/transition}

