The two major categories of cartography are general cartography and thematic cartography, which are introduced in chapter \ref{s:cartography} on page \pageref{s:cartography}. This categorization can be directly adopted from cartography to maps. The main objective of this chapter is to give an overview of different thematic maps and their usage. These maps can be subdivided into univariate and multivariate maps.

\paragraph{Univariate Thematic Map Types}
\label{s:univariate-maps}

Univariate maps are only dependent on one variable, except for the map variables like latitude and longitude. This section contains four different univariate maps and is going to explain them in detail.

% TODO: all subsections should be presented in Alphabet of visualisations; "dot as visual mark", "symbol as visual mark"
\subparagraph{Dot density map}
\label{s:dot}
\input{chapters/methods/cartography/univariate/dot}

\subparagraph{Graduated symbol or proportional symbol map}
\input{chapters/methods/cartography/univariate/psm}

\subparagraph{Choropleth map}
\input{chapters/methods/cartography/univariate/choropleth}
\label{s:choropleth}

\subparagraph{Cartogram}
\input{chapters/methods/cartography/univariate/cartogram}

\paragraph{Multivariate Thematic Map Types}
Multivariate maps are dependent on multiple variables. This section will only give an overview of bivariate maps for the sake of convenience of this type and will not explain them in detail. Some of these maps can be used univariate and multivariate and therefore are not discussed again if they are alreay explained in detail in chapter \ref{s:univariate-maps} on page \pageref{s:univariate-maps}. However, the needed information to understand limitations and concerns are still added.

\subparagraph{Bivariate Proportional Symbol Map}
\input{chapters/methods/cartography/multivariate/psm}

\subparagraph{Bivariate Choropleth Map}
\input{chapters/methods/cartography/multivariate/choropleth}

\subparagraph{Bivariate Cartogram}
\input{chapters/methods/cartography/multivariate/cartogram}