%add more about generating data and data overall
There has never been such a quantity of data available in history and the global amount of information has never grown so fast. Every day 2.5 Exabytes of new data is generated and by 2020 an annual growth of 35 Zettabytes is predicted \iacite{IBM.2013}. Most scientific experiments and simulations of different types like chemistry, medicine or physics generate more and more data. ``The Large Hadron Collider'' of CERN in Genf produced 13 petabytes of data in 2010 \iacite{Brumfield.2011}. Economy, especially merchandise trade generates data in large measures. Each and every one of us generates data every day. Partly, this happens knowingly with activities in social media \textendash\ Facebook alone produces 500 Terabytes every day \iacite{Tam.2012} \textendash\ but we constantly produce data with various sensors in our smartphones.

%add more about information overload and turning information into knowledge
Processing and analysis of data garners increased economic and scientific interest. Searching for useful and usable information is commonly known as ``Data Mining''.

Despite recent technical advantages of search engines and content provider services the information overload problem still remains a crucial issue for many application fields. Finding the right piece of information in huge information spaces is a tedious and time consuming task. Visualisations have shown to be an effective way to deal with the overload issue providing the possibility to display and explore a huge set of data points at the same time. However, creating useful visual representations of data typically requires domain knowledge \iacite{Nazemi.2013}.

% Assume a dataset including retail information.
For example, assuming a visualisation about e-commerce data exists, there is often the problem that it is not intuitive and easy to understand. If a shop wants to find out where to open their next warehouse in order to provide a better delivery service, it is mandatory to find out where most of the orders come from. For this type of task, multiple types of visualisations exist. Using thematic cartography is one way to address the given task. Displaying all orders in a map results in constructing first knowledge about the geographic distribution, which could already be sufficient. However, there are many different thematic maps in the field of cartography and some may not be as appropriate as others. Giving users control to change the visual appearance may be sufficient to satisfy their needs. Additionally, animating the transition between appropriate visual appearances could result in a better readability of each visualisation.
% Considering the aforementioned task, every thematic map has a certain use-case and animating the transition between maps could support the understanding of the primal use-case of the map.

Thus the importance of the field of visualisation grows with the amount of generated data. Visualisation utilises the human capability of understanding pictures better than numbers. It allows the discovery of knowledge in data that would not be possible with other means. Maps are most efficient in enabling perspicuity of complex situations. They can be seen as an interface between a user and the data. Thus, enabling them to answer location-related questions \iacite{Gartner2013}.